
\documentclass{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.50.0.2953}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=Manual}
%TCIDATA{Created=Tuesday, October 29, 2024 12:08:55}
%TCIDATA{LastRevised=Tuesday, October 29, 2024 12:10:27}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{<META NAME="DocumentShell" CONTENT="Standard LaTeX\Blank - Standard LaTeX Article">}
%TCIDATA{CSTFile=40 LaTeX article.cst}

\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{solution}[theorem]{Solution}
\newtheorem{summary}[theorem]{Summary}
\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
\input{tcilatex}

\begin{document}


\begin{thebibliography}{99}
\bibitem{balgetir} Balgetir, H., Bekta\c{s}, M., Inoguchi, J.(2004) Null
Bertrand Curves in Minkowski 3-Space and their characterizations. Note Mat.,
23, 7--13.

\bibitem{bertrand} Bertrand, J. Memoire sur la theorie des courbes a double
courbure, Journal de Mathematiques Pureset Appliquees, 15 (1850), 332--350.

\bibitem{kilicoglu} K\i l\i \c{c}oglu, \c{S}., \c{S}enyurt, S. (2020). On
The Curves $N-T^{\ast }N^{\ast }$ in E$^{3}$. Turk. J. Math. and Comp. Sci.,
12 (2), 161-165. DOI: 10.47000/tjmcs.616122

\bibitem{huseyin k} Kocayi\u{g}it, H., \"{O}nder, M., Hacisalihoglu, H.H.
(2014). Harmonic 1-Type Curves and Weak Biharmonic Curves in Lorentzian
3-Space, Ana. Stiin. A. Uni. Al. I. Cuza. D. I. (S.N.) Mat., 1, 109--124.

\bibitem{es} Lone M. S., Es H., Karacan M. K, Bukcu B., Mannheim curves with
modified orthogonal frame in Euclidean 3-space, Turk. J. Math., 43 (2019),
648--663.

\bibitem{matsuda} Matsuda, H. and Yorozu, S.(2003), Notes on Bertrand
curves, Yokohama Mathematical Journal, 50:41--58.

\bibitem{oztekin} \"{O}ztekin, H. B. and Bekta\c{s}, M. (2010),
Representation formulae for Bertrand curves in the Minkowski 3-space,
Scientia Magna, 6: 89-96.

\bibitem{struik} Struik, D. J., Lectures on Classical Differential Geometry,
Dover Publications, 1988.

\bibitem{senyurt} \c{S}enyurt S., Bekta\c{s} \"{O}. (2012),
Timelike-spacelike Mannhe\i m partner curves in $R_{1}^{3},$International J.
Physical Sciences, 7(1) 100-106.

\bibitem{beyhan} Y\i lmaz, B. (2021), Some curve pairs according to types of
Bishop frame. AIMS Mathematics, 6(5): 4463-4473. doi: 10.3934/math.2021264
\end{thebibliography}

\end{document}
